% !TEX program = pdflatex
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nico Ohayon} \\ \vspace{1pt}
    \small 469-560-0141 $|$ \href{mailto:x@x.com}{\underline{nohayonr@gmail.com}} $|$ 
    \href{https://linkedin.com/in/nico-ohayon-rozanes}{\underline{linkedin.com/in/nico-ohayon-rozanes}} $|$
    \href{https://github.com/NicoOhR}{\underline{github.com/NicoOhR}}$|$
    \href{https://nicoohr.github.io/Sicarii}{\underline{Portfolio}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Dallas}{Richardson, TX}
      {Bachelor of Science in Data Science, Double Degree in Mathematics}{Aug. 2023 -- May 2027}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{May 2025 -- Aug 2025}
      {Exolambda}{Richardson, TX}
      \resumeItemListStart
      \resumeItem{Helped bring up and test new avionics boards, finding and fixing issues before customer demos.}
      \resumeItem{Built communication stack and sensor pipeline (ADC/IMU) which reduced latency by 40\% and increased bandwidth}
      \resumeItem{Wrote real-time control and signal processing code that met strict latency targets in bench tests.}
      \resumeItem{Cleaned up and standardized the embedded build system, cutting set time and reducing deployment complexity}
      \resumeItem{Worked with hardware and controls teams to validate flight-test algorithms}
    \resumeItemListEnd
    \resumeSubheading
      {Bioinformatics Research Assistant}{August 2025 - Present}
      {University of Texas at Dallas}{Richardson, TX}
      \resumeItemListStart
      \resumeItem{Analyze high-frequency mouse IMU data to detect early movement changes linked to disease.}
      \resumeItem{Improved unsupervised clustering workflow, increasing stability and eliminating memory errors from legacy code.}
      \resumeItem{Accelerated similarity calculations with GPU methods, shrinking runtime from 12 hrs to 3 hours.}
      \resumeItem{Built time-series preprocessing that improved behavior separation and interpretability.}
      \resumeItem{Created reproducible experiment tracking and docs, enabling parameter sweeps with clear comparisons.}
    \resumeItemListEnd
    \resumeSubheading
    {Embedded Subteam Lead}{December 2023 - December 2024}
    {Dallas Formula Racing}{Richardson, TX}
    \resumeItemListStart
    \resumeItem{Led firmware and electronics for data acquisition and displays on the 2024 cars, supporting 12 critical sensors and an additional 4 auxiliary.}
    \resumeItem{Ran weekly meetings and reviews, keeping a team of 12 engineers on schedule through design and track testing.}
    \resumeItemListEnd
    \resumeSubheading
      {Undergraduate Research Scholar Award}{August 2024 -- December 2024}
      {University of Texas at Dallas}{Richardson, TX}
      \resumeItemListStart
      \resumeItem{Studied Latin square transversals with Prof.\ Bereg, validating results from prior work.}
      \resumeItem{Built fast C++ search code that handled matrices by pruning impossible cases.}
      \resumeItem{Ran large computational experiments and summarized patterns that informed follow-up conjectures.}

      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{TradeX} $|$ \emph{Python, PyTorch, NumPy, Docker}}{January 2024 - May 2024}
          \resumeItemListStart
          \resumeItem{Found strongly related stock pairs for trading ideas using correlation-based network methods.}
          \resumeItem{Built clean return datasets and dependency estimates to support pair selection.}
          \resumeItem{Tested strategies in simulation, outperforming baseline by 40\%.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{FSAEStats} $|$ \emph{Rust, DuckDB, Arrow}}{}
          \resumeItemListStart
          \resumeItem{Automated pulling race results from PDFs into structured datasets.}
          \resumeItem{Built a fast and scalable Rust big-data backend for querying race data based on Apache Arrow and DuckDB.}
          \resumeItemListEnd
                \resumeProjectHeading
          {\textbf{Three Body Simulation} $|$ \emph{Rust, Tokio, Python, gRPC, PyTorch, Bevy}}{}
          \resumeItemListStart
          \resumeItem{Built a three-body physics simulator in Rust to study stability, collisions, and escape cases, visualizing trajectories in real time.}
\resumeItem{Added a gRPC interface so external tools, Python in this case, could run scripted experiments, enabling [N]+ automated trials and faster research iteration.}

          \resumeItemListEnd

    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Rust, Python, GoLang, \LaTeX} \\
     \textbf{Tools}{: Linux, BusyBox, Yocto, Kafka, Docker, Git, GitHub Actions, CMake} \\
     \textbf{Data/Machine Learning}{: SQL, NumPy, pandas, CUDA, scikit-learn, PyTorch, Matplotlib/Seaborn, DuckDB, Apache Arrow}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
