% Cover letter using letter.cls
\documentclass{letter}
%\usepackage{helvetica} % uses helvetica postscript font (download
% helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=6in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{N. Ohayon Rozanes}                  % name for signature
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left

\begin{letter}{}

  \begin{center}
    {\large\bf N. Ohayon Rozanes} \\
    {611 Granbury Dr. \\ Allen, Texas, 75013  \\ 469-560-0141}
  \end{center} \vfill % forces letterhead to top of page

  \opening{Dear Hiring Manager:}

  \noindent I am writing to apply for the Laboratory Automation Software
  Internship for Summer 2026 at Calico.  I am pursuing double degree
  Data Science and Mathematics at the university of Texas at Dallas,
  with a strong focus on building reliable software systems that interact
  directly with physical hardware.

  \noindent My background closely aligns with teh Automation Core
  team's work at the boundary of software and laboratory instrumentation.
  Through my work at the FSAE club on campus, academic research
  laboratories, and an embedded systems internship  I have extensive
  experience developing software which lives close to the hardware,
  and have experience  deploying software to physical environments.

  \noindent In my current research lab, my primary responsibility is
  working with the graduate students and lab technicians to replace ad hoc
  workflows with reproducible systems. For example, I built the system
  which syncs together the recording and sensor measurment of the lab
  subjects. Recently, I have been working on automating the file
  management regiment that a grad student developed, and migrating the lab
  to a database rather than loose files, as we have been doing so
  far. This work has emphasized careful API design, clear ownership of
  state, and defensive programming to accommodate evolving experimental needs.

  \noindent Other than a matching skill set, Calico's mission
  statement is incredibly compelling. I would like to write code
  towards something that matters, which feels difficult in the
  context of the software industry; to that end, I think Calico
  offers the opportunity to support research in an active and
  actuatable manner. One of the things that we maybe take for granted
  as software people is the world class quality of our tools, and I
  would be ecstatic to work at Calico towards improving the tools of
  scientists.

  \noindent I would welcome the opportunity to contribute to Calico’s Automation
  Core team and to learn from engineers and scientists working at the forefront
  of aging research.

  \closing{Sincerely yours,}
\end{letter}

\end{document}
